Presentation Title

### 2017-08-08 paper/s3-system.tex
Give paper a structure

\chapter{System architecture}
\label{ch:model}

% As was shown in~\Cref{ch:problem}, the requirements are the following.
% \begin{itemize}
%     \item Global consensus
%     \item Security and fault tolerance
%     \item Performance and scalability
% \end{itemize}

% As mentioned in the Introduction, the primary goal is performance and scalability.
% Having a scalable blockchain system while still keeping global consensus
% allows the system to be ubiquitous and realise the full potential of blockchain.

% The secondary goal is to design an application neutral system.
% In particular, it should act as a backbone that provides the building blocks of blockchain based applications.
% It should be possible to buld any kind of application on top our system.
% Further, we do not impose on a consensus algorithm, as long as it satisfies the properties of atomic broadcast which we describe in~\Cref{sec:overview-cons}.

% The third and final goal is security.
% Our system should be unaffected in the presence of powerful adversaries.
% In particular, adversaries are Byzantine meaning that they can have arbitrary behaviour.
% Thus anything is possible from simply ommitting messages to colluding with eachother in order to undermine the whole system.

@@

The goal of this chapter is to detail our system specification.
We begin our discussion with an intuitive overview of the architecture in \Cref{sec:system-overview}.
Next, we give the formal description, starting with the model and assumptions in \Cref{sec:model-assumptions}.
Then, the three protocols which make up the complete system,
namely consensus protocol (\Cref{sec:cons-protocol}), transaction protocol (\Cref{sec:tx-protocol}) and validation protocol (\Cref{sec:vd-protocol}).
Finally, we discuss a few variations of our main design and their respective tradeoffs in \Cref{sec:tradeoffs}.

\section{System overview}
\label{sec:system-overview}
The architecture is visualised in~\Cref{fig:architecture}.
\begin{figure}[h]
\centering
\includegraphics[width=0.7\textwidth]{architecture}
\caption{Overview of the system architecture}
\label{fig:architecture}
\end{figure}
It consists of one data structure---Extended TrustChain, and three protocols.
The protocols have distinct roles which are evident from their names.
They run concurrently and do not interact with each other.
The only synchronization happens on the Extended TrustChain layer, where all the protocols read and write from it.
We first describe each component individually, starting with Extended TrustChain, and then explain how they fit together.

\subsection{Extended TrustChain}
Extended TrustChain naturally builds on top of the standard TrustChain. 
Thus we first describe the standard TrustChain.
Our description has minor differences compared to the description in~\cite{multichain}.
This is to help with the description of the extended TrustChain.
We remark the difference when it occurs.
However, the two descriptions are functionally the same.

\subsubsection*{Standard TrustChain}
In TrustChain, every node has a ``personal'' chain. 
Initially, the chain only contains a genesis block generated by the nodes themselves.
When a node $A$ wishes to add a new transaction (TX) with $B$,
a new TX block is generated for both $A$ and $B$ and is appended to their respective chains.
The TX block must have a valid hash pointer pointing to the previous block
and a reference\footnote{This is different from the original TrustChain definition found in~\cite{multichain}.
In there, a TX block has two outgoing edges which are hash pointers to the two parties involved in the transaction.
This work uses one outgoing edge and a reference.} to its \emph{pair} on $B$'s chain.
An example of is shown in \Cref{fig:trustchain-bad}.

\begin{figure}
    \includegraphics[width=0.9\textwidth]{trustchain-bad}
    \centering
    \caption{Every block is denoted by $t_{i,j}$, where $i$ is the node ID and $j$ is the sequence number of the block.
    Thus we have three nodes and three corresponding chains in this example.
    The arrows represent hash pointers and the dotted lines represent references.
    The blocks at the ends of one dotted line are pairs of each other.
    The red block after $t_{b, 5}$ indicates a fork.}
    \label{fig:trustchain-bad}
\end{figure}

If every node follows the rules of TrustChain and we only consider hash pointers and not references,
then every chain effectively forms a singly linked list.
However, if a node violates the rules, then a \emph{fork} may happen.
That is, there may be more than one TX block with a hash pointer pointing back to the same block.
In \Cref{fig:trustchain-bad}, node $b$ (in the middle chain) created two TX blocks that both point to $t_{b, 5}$.
If this is a ledger system it can be seen as a double spend, where the currency accumulated up until $t_{b, 5}$ is spent twice.

\subsubsection*{Extended TrustChain}
We are now ready to explain the Extended TrustChain.
The primary difference is the introduction of a new type of block---checkpoint (CP) block.
In contrast to TX blocks, CP blocks do not store transactions or contain references.
Their purpose is to capture the state of the chain and the state of the whole system.
In particular, the state of the chain is captured with a hash pointer.
The state of the whole system is captured in the content of the CP block,
namely as a digest of the latest \emph{consensus result} which we explain in \Cref{sec:overview-cons}.
A visual representation is shown in \Cref{fig:trustchain-bad-cp}.

From this point on, we use TrustChain to mean the Extended TrustChain unless explicitly clarified.

\begin{figure}
    \includegraphics[width=0.9\textwidth]{trustchain-bad-cp}
    \centering
    \caption{The circles represent CP blocks,
    they also have hash pointers (arrow) but do not have references (dotted line).
    Note that the sequence number counter do not change, it is shared with TX blocks.}
    \label{fig:trustchain-bad-cp}
\end{figure}

\subsection{Consensus protocol}
\label{sec:overview-cons}

% The consensus protocol uses an existing Byzantine consensus algorithm (explained in detail in \Cref{sec:xyz}) and runs it continuously in rounds.
The consensus protocol can be seen as a technique of running infinitely many rounds of some 
Byzantine consensus algorithm\footnote{More accurately it is ACS or asynchronous subset consensus, we describe ACS in \Cref{sec:acs-background}.},
starting a new execution immediately after the previous one is completed.
This is necessary because blockchain systems always need to reach consensus on new values proposed by nodes in the system,
or CP blocks in our case.

The high communication complexity of Byzantine consensus algorithms prohibits us from running it on a large network.
Thus, for every round, we randomly select some node---called facilitators---to collect CP blocks from every other node and use them as the proposal.
The facilitators are elected using a \emph{luck value}, which is computed using $\textsf{H}(\C_r || pk_u)$,
where $\C_r$ is the consensus result 
(which can be seen as the set union of all the CP blocks collected by the facilitators)
in round $r$ and $pk_u$ is the public key of node $u$.
Intuitively, the election is guaranteed to be random 
because the output of a cryptographically secure hash function is unpredictable and $\C_r$ cannot be determined in advance.
Finally, the elected facilitators run a Byzantine consensus algorithm to agree on a set of CP blocks.
The next round begins when the new facilitators are computed from these CP blocks.

A visual explanation can be found in \Cref{app:consensus-example},
it walks through the steps needed for a node to be selected as a facilitator using an example.

\subsection{Transaction and validation}
The TX protocol is a simple request and response protocol.
The nodes exchange one round of messages and create new TX blocks on their respective chains.
Thus, as we mentioned before, one transaction should result in two TX blocks.

The consensus and transaction protocol by themselves do not provide a mechanism to detect tampering.
Thus we need a validation protocol to counteract malicious behaviour.
When a node wishes to validate one of its TX, it asks the counterparty for the \emph{agreed fragment} of the TX.
An agreed fragment of a TX block is a section of the chain beginning and ending with CP blocks that contain the TX block,
the CP blocks must also be in consensus.
Upon the counterparty's response, the node checks that the CP blocks are indeed in consensus,
the hash pointers are valid and his TX is actually in the fragment.
The TX is valid if these conditions are satisfied.
Intuitively, this works because it is hard (because a cryptographically secure hash function is second-preimage resistant)
to create a different chain that begins and ends with the same two CP blocks.

\subsection{Combined protocol}
\label{sec:combined-protocol}
The final result is essentially the concurrent composition of the three aforementioned protocols,
all making use the Extended TrustChain data structure.

Our sub-protocol design gives us the highly desirable non-blocking property.
In particular, we do not need to ``freeze'' the state of the chain for some communication to complete in order to create a block.
For instance, a node may start the consensus protocol, and while it is running, create new transactions and validate old transactions.
By the time the consensus protocol is done, the new CP block is added to whatever the state that the chain is in.
It is not necessary to lock the chain while the consensus protocol is running and then unlock it afterwards.

\section{Model and assumptions}
\label{sec:model-assumptions}

@@

\section{Extended TrustChain}
The primary data structure used in our system is the Extended TrustChain.
Each node $u$ has a public and private key pair---$pk_u$ and $sk_u$, and a chain $B_u$.
The chain consist of blocks $B_u = \{ b_{u, i} : i \in \{ 0, \dots, h - 1 \} \}$,
where $b_{u, i}$ is the $i$th block of $u$,
and $h$ is the height of the block (i.e. $h = |B_u|$).
We often use $b_{u, h}$ to denote the latest block.
There are two types of blocks, TX blocks and CP blocks.
If $T_u$ is the set of all TX blocks in $B_u$ and $C_u$ is the set of all CP blocks is $B_u$,
then it must be the case that $T_u \cup C_u = B_u$ and $T_u \cap C_u = \varnothing$.
The notation $b_{u, i}$ is generic over the block type.
We assume there exists a function $\textsf{typeof}: B_u \rightarrow \{ \tau, \gamma \}$ that returns the type of the block,
where $\tau$ represents the TX type and $\gamma$ represents the CP type.

@@

% The length of the fragment is constrained by $L$,
% namely $\forall t |\textsf{fragment}(t)| \le L$.
% The purpose to prevent spam and encourage nodes to create more CP blocks.
% $L$ should be sufficiently high so that busy nodes are not hindered by it.

\section{Consensus protocol}
\label{sec:cons-protocol}

Our scalable consensus protocol runs on top of Extended TrustChain.
It uses an unmodified asynchronous subset consensus (ACS) algorithm as the key building block.
The objectives of the protocol are to
    allow honest nodes always make progress (in the form of creating new CP blocks),
    compute correct consensus result in every round
    and have an unbiased election of facilitators.
Concretely, we define the necessary properties as follows.
\begin{definition}
\label{def:consensus}
\textbf{\emph{Properties of the consensus protocol}}

$\forall r \in \mathbb{N}$, the following properties must hold.
\begin{enumerate}
    \item \emph{Agreement}:
        If one correct node outputs a set of facilitators $\F_r$,
        then every node outputs $\F_r$
    \item \emph{Validity}:
        If any correct node outputs $\F_r$, then 
            \begin{enumerate}
                \item $|\C_r| \ge N - t$ and each CP in $\C_r$ belong to a different node\footnote{
                $\C_r$ is a tuple but we abuse the notation here by writing $|\C_r|$ to mean the number of CP blocks in the second element of $\C_r$.}.
                \item $\F_r$ must contain at least $n - t$ honest nodes and
                \item $|\F_r| = n$.
            \end{enumerate}
    \item \emph{Fairness}:
        Every node with a CP block in $\C_r$ should have an equal probability of becoming a member of $\F_r$.
    \item \emph{Termination}:
        Every correct node eventually outputs some $\F_r$.
\end{enumerate}
\end{definition}
These properties may look like Byzantine consensus properties (which we describe next in \Cref{sec:acs-background}) but there are subtle differences.
Firstly, they are properties for every node in the network and not just the facilitators.
Secondly, they must be satisfied for all rounds because the whole system falls apart if one of the property cannot be satisfied in one of the rounds.

Before describing the protocol in detail,
we take a brief detour to give background on the ACS algorithm as it is the primary building block.
Then we move on to describe the two phases of our consensus protocol---bootstrap phase and consensus phase.

\subsection{Background on asynchronous subset consensus}
\label{sec:acs-background}

The best way to explain ACS is to contrast it with the typical Byzantine consensus.
We adapt the description from~\cite[Chapter 17]{podc}.
%The Byzantine consensus problem is a classical problem is distributed systems literature.
%It is first described by Leslie Lamport as the Byzantine general's problem in 1982~\cite{lamport1982byzantine}.
%Byzantine consensus is described as follows (adapted from ).
\begin{definition}
\textbf{\emph{Byzantine consensus}}

There are $n$ nodes, of which at most $t$ might experience Byzantine fault.
Node $i$ starts with an input value $v_i$.
The nodes must decide for one of  those values, satisfying the following.
\begin{enumerate}
    \item \emph{Agreement:}
        If a correct node outputs $v$, then every node outputs $v$.
    \item \emph{Validity:}
        The decision value must be the input value of a node.
    \item \emph{Termination:}
        All correct nodes terminate in finite time.
\end{enumerate}
\end{definition}
A node under Byzantine fault means that it can have arbitrary behaviour.
For example not sending a message or colluding with other Byzantine nodes to undermine the entire system.
Note that the decision is on a single value.
This is in contrast to ACS which we describe next.

ACS is an especially useful primitive for blockchain systems.
It allows any party to propose a value and the result is the set union of all the proposed values by the majority.
Concretely, ACS needs to satisfy the following properties (adapted from~\cite{miller2016honey}).
\begin{definition}
\label{def:acs}
\textbf{\emph{Asynchronous subset consensus}}

There are $n$ nodes, of which at most $t$ might experience Byzantine fault.
Node $i$ starts with a non-empty set of input values $C_i$.
The nodes must decide an output $C$, satisfying the following.
\begin{enumerate}
    \item \emph{Agreement:}
        If a correct node outputs $C$, then every node outputs $C$.
    \item \emph{Validity:}
        If any correct node outputs a set $C$,
        then $|C| \ge n - t$ and $C$ contains the input of at least $n - 2t$ nodes.
    \item \emph{Totality:}
        If $n - t$ nodes receive an input, then all correct nodes produce an output.
\end{enumerate}
\end{definition}

ACS has the nice property of censorship resilience when compared to other consensus algorithms.
For instance, Hyperledger and Tendermint uses a variant of Practical Byzantine Fault Tolerance (PBFT)~\cite{castro1999practical} as their consensus algorithm.
In PBFT, a leader is elected, if the leader is malicious but follows the protocol, then it can selectively filter transactions.
In contrast, every party in ACS are involved in the proposal phase,
and it guarantees that if $n - 2t$ parties propose the same transaction, then it must be in the agreed output.
Thus, if some value is submitted to at least $n - 2t$ nodes, it is guaranteed to be in the consensus result.
For a detailed description of ACS, we refer to the HoneyBadgerBFT work~\cite{miller2016honey}.
To understand the remainder of this work, the knowledge of~\Cref{def:acs} is sufficient.

The main drawback with ACS and also Byzantine consensus algorithms is the high message complexity.
Typically, such protocols have a message complexity of $O(n^2)$, where $n$ is the number of parties.
Hence, it may work with a small number of nodes,
but it is infeasible for blockchain systems where thousands of nodes are involved.

% The literature on Byzantine consensus and atomic broadcast is rich, some noteable ones include TODO.
% Thus in the ETC consensus protocol, we assume there exist an "off-the-shelf" Byzantine consensus algorithm which we can use
% (in our implementation we use HoneyBadgerBFT and motivate our choice in TODO).

% In our case, every node do not propose some arbitrary data, but a set of CP blocks.
% Thus the result of the consensus is the set union of all the legitimate proposals.

\subsection{Bootstrap phase}
\label{sec:bootstrap}
Now we have all the necessary information to describe our consensus protocol.
As with all distributed systems, there must be a bootstrap phase which sets up the system.

@@

\subsection{Consensus phase}
\label{sec:consensus-phase}
The consensus phase begins when $\F_r$ is available to all the nodes.
Note that $\F_r$ indicates the facilitators that were elected using results of round $r$ and are responsible for driving the ACS protocol in round $r + 1$.
The goal is to reach agreement on a set of new facilitators $\F_{r + 1}$ that satisfies the four properties in \Cref{def:consensus}.

@@

\section{Transaction protocol}
\label{sec:tx-protocol}

@@

\section{Validation protocol}
\label{sec:vd-protocol}

@@

\subsection{Validity definition}
A transaction can be in one of three states in terms of validity---\emph{valid}, \emph{invalid} and \emph{unknown}.
Given a fragment $F_{v, j}$, the validity of the TX block $t_{u, i}$ and the agreed fragment of it is captured by the function $\textsf{get\_validity}(t_{u, i}, F_{u, i}, F_{v, j})$ (\Cref{alg:get-validity}).
Note that $t_{u, i}$ and $F_{u, i}$ are assumed to be valid,
otherwise the node calling the function would have no point of reference.
This is not difficult to achieve.
Typically the caller is $u$, so it knows its own TX block and the corresponding agreed fragment.
If the caller is not $u$, it can always query for the agreed fragment that contains the transaction of interest from $u$.

@@

\begin{algorithmic}[1]

@@

\subsection{Validation protocol}
Our validation protocol,
shown in~\Cref{alg:vd-proto},
is designed to classify transactions according to the aforementioned validity definition.
If $u$ wishes to validate some TX with ID $txid$ and counterparty $v$, it sends $\langle \texttt{vd\_req}, txid \rangle$ to $v$.
The desired properties of the validation protocol are as follows.
\begin{definition}
\label{def:validation}
\textbf{\emph{Properties of the validation protocol}}

@@

\section{Design variations and tradeoffs}
\label{sec:tradeoffs}

@@

\subsection{Using epidemic protocol to reduce communication cost}
One of the final steps in our consensus protocol is to broadcast the consensus result and signatures to every other node (\Cref{sec:consensus-phase}).
While this guarantees delivery (since we assumed reliable channel), it is wasteful.
For example, if every facilitator is honest, a node would receive $n$ consensus results which are identical when only one is necessary.
Furthermore, realistic networks do not offer a broadcast primitive,
i.e. firewalls may block incoming messages from certain nodes.

@@

\subsection{Using timing assumption in the permissionless setting}
\label{sec:permissionless}
Our model is purely asynchronous, where we make no timing assumptions anywhere in the protocol.
However, in many applications it is often fine to make timing assumptions.
For example, TCP relies on timeout for its retransmission and the \texttt{nLockTime} property in Bitcoin transactions makes the transaction unspendable until some time in the future (either Unix time or block height)~\cite{bitcoindevguide}.
One limitation of our system is that we use the parameter $N$ in our algorithms, which makes it unsuitable for the permissionless environment where users can join and leave at will.
In this section we show how making a timing assumption would allow us to operate in the permissionless setting.

@@

\subsection{Privacy preserving validation protocol using compact blocks}
\label{sec:compact}
Our approach already has privacy preserving features in comparison to early blockchain systems.
That is, the transactions for each node are only revealed during the validation protocol.
Hence if two nodes never directly or indirectly interact with each other,
their transactions are never revealed.

We can take our privacy-preserving property one step further by introducing another level of hash pointer indirection.
The result is shown in~\Cref{fig:compact}.
\begin{figure}
    \includegraphics[width=0.7\textwidth]{compact}
    \centering
    \caption{The chain on the left represent direct chaining, where the digest in ``Prev'' is simply the digest of the previous block.
    The chain on the right uses compact blocks, represented by the smaller squares.
    Compact blocks also form a chain as before, but they each have a hash pointer to the full block, identified by ``Seq'' and ``Digest''.}
    \label{fig:compact}
\end{figure}

@@

\subsection{Optimising validation protocol using cached agreed fragments}
\label{sec:caching}
One more way to improve the efficiency of the validation protocol is to use a single agreed fragment to validate multiple transactions.
Concretely, upon receiving an agreed fragment from node $A$,
rather than validating a single transaction,
we attempt to validate all transactions with $A$ in the unknown state in that fragment.

@@

\subsection{Global fork detection}
The validation algorithm guarantees that there are no forks within a single agreed fragment.
This is sufficient for some applications such as proving the existence of some information.
However, for applications such as digital cash where every block depends on one or more previous blocks,
our scheme is not suitable.
For such applications, we need to guarantee that there are no forks from the genesis block leading up to the TX block of interest.

@@

% TODO?
% \subsection{Secure txid generation using a commitment protocol}

% subtlety when fork happens on CP block

% Another assumption we made in this work is the existance of a PKI.
% This can also be removed with the introduction of timing by storing the public keys the consensus results,
% much like in Bitcoin.

% \section{Universally Composable Framework}
% \label{sec:uc-intro}

% In order to analyse the security of a system, a formal notion of security is required.
% For instance, what does it mean if an encryption algorithm is secure?
% One may say it is secure if the adversay cannot learn any information about the plaintext from the ciphertext.
% But what if the adversay has some background information, for instance she may know it is English.
% Do we then still say the encryption algorithm is secure?
% Goldwasser and Micali introduced the notion of semantic security~\cite{goldwasser1982probabilistic}.
% That is, imagine two worlds, a real world and an ideal world.
% In the real world, the adversay is given the ciphertext,
% and in the ideal world the adversay has nothing.
% Then the encryption algorithm is semantically secure if the amount of information that the adversay can learn in the real world is just as much as the ideal world.
% While our description is informal, the notion of security can be formally captured in this way.

% Security sensitive distributed systems such as secure multi-party computation and blockchain systems also require a formal notion of security so that they can be analysed.
% Fortunately, the idea from semantic security can also be applied in a distributed setting.
% In an ideal world, we create an ideal functionality $\Fideal$ that performs all the computation on behalf of every node in the network.
% The nodes act as dummies and only relay messages between $\Fideal$ and the environment.
% Thus $\Fideal$ essentially becomes the specification of the distributed protocol.
% If the execution of the real world protocol is indistinguishable from the ideal emulation in the presence of some adversay,
% then the real world protocol is secure as per the ideal specification.
% This is in essence the Universally Composable (UC) framework.

% We use the UC framework not only because it suits our needs, 
% it is also the only framework used in modelling blockchain systems to the best of our knowledge
% ~\cite{todo}TODO.
% In the remainder of this section we give an overview of the UC framework.
% A detailed treatment  can be found in~\cite{canetti2001universally}.

% \subsection{Model of Computation}
% The model of computation considered in the UC framework is the interactive Turing machine (ITM).
% Specifically, an ITM is an extension of the Turing machine with externally writable tapes which are the following.
% \begin{enumerate}
% \item input tape---TODO
% \item incoming communication tape---TODO
% \item subroutine output tape---TODO
% \end{enumerate}
% ITM can be seen as a specification or an algorithm, a machine running an ITM is an ITM instance (ITI).
% To communicate, an ITI can write on the externally writable tapes of other ITIs.
% The writing ITI then pauses exeuction, the receiving ITI begins execution.
% Consequently, only one ITI is running at any point in time.

% \subsection{Simulation-based Security}
% Simulation-based security, also known as ideal/real paradigm is a model for defining security.
% The model consist of a set of , the environment $\E$, the adversay $\A$,
% the protocol ITM $\Preal$ and zero or more ideal functionalities $\mathcal{F}_0, \mathcal{F}_1, \dots$.
% The 
% Other than the machines running the protocol under consideration, the model contains two extra entities,
% the environment $\E$ and the adversary $\A$.
% $\E$ can be seen as users of the protocol, it can only provide input and receive output from $\A$ and the protocol.

% Control function TODO

% \subsection{Universal Composability}

% \section{Formal Specification}
% \label{sec:formal-model}

% The formal model follows the same structure as \ref{fig:todo}TODO.

% \begin{figure}[h]
% \begin{framed}
% \small  % end with \normalsize

% \textbf{Protocol}\,$\Preal$

% The ETC protocol. On initialisation do the following.
% \begin{itemize}
% \item Generate public and private key pair, $pk$ and $sk$.
% \item Set personal chain $C := \{genesis()\}$.
% \item Set checkpoint buffer $\C' := \varnothing$.
% \item Set the facilitators $F$ to the bootstrap nodes provided by $\E$.
% \item Set the latest round $r_{\text{latest}} = 0$.
% \end{itemize}

% Run the protocol as specified below after initialisation.
% \begin{itemize}

% \item Upon (\texttt{consensus}, $D$) from $\F^r_\text{BFT}$,
%     if $r_{\text{latest}} >= r$ then do nothing and pause,
%     otherwise do $try_add_cp(D, r)$
%     send (\texttt{propose})

% \item Upon (\texttt{consensus}, $D$, $r$) from $p \in \P$,

% \item Upon (\texttt{checkpoint}, $c$) from $p \in \P$,

% \item Upon (\texttt{tx\_init}, $m$, $p$) from $\E$, 
%     $C := C \cup \{new\_tx(m)\}$,
%     send (\texttt{tx\_req}, latext TX in $C$) to $p$.

% \item Upon (\texttt{tx\_req}, $m$) from $p \in \P$,
%     $C := C \cup \{new\_tx(m)\}$,
%     let $m'$ be the latest TX in $C$ and set $m$ to be the other half of $m'$,
%     send (\texttt{tx\_resp}, $m'$) to $p$.
%     Output the complete TX to $\E$.

% \item Upon (\texttt{tx\_resp}, $m'$) from $p \in \P$,
%     find the corresponding pair of $m'$ and name it $m$,
%     add $m'$ as the other half of $m$.
%     Output the complete TX to $\E$.

% \item Upon (\texttt{vd\_init}, $s$) from $\E$,
%     if the sequence number $s$ does not exist in $C$ or the block with $s$ does not have the other half then do nothing.
%     Otherwise send (\texttt{vd\_req}, $s'$) to $p'$ where $s'$ is the sequence number of the other half and $p'$ is the counterparty.

% \item Upon (\texttt{vd\_req}, $s'$) from $p \in \P$,
%     if the sequence number $s'$ does not exist then do nothing.
%     Otherwise send (\texttt{vd\_resp}, $agreed\_fragment(s')$) to $p$.

% \item Upon (\texttt{vd\_resp}, $x$) from $p \in \P$,
%     run $validate(x)$ and output result to $\E$.

% \end{itemize}

% \normalsize
% \end{framed}
% \end{figure}

% \begin{framed}
% \textbf{Functionality}\,$\F^r_\text{BFT}$

% The ideal Byzantine consensus protocol, parameterised by the round number $r$.

% \begin{itemize}
% \item Upon (\texttt{propose}, $r$, $C$),
% \item Upon (\texttt{fetch}),
% \end{itemize}
% \end{framed}

% \subsection{Discussion}

% \subsubsection{Global clock for synchronization}
% Where there is no Byzantine corruption, we conjecture that our protocol runs in the asynchronous setting.
% However, security of many Byzantine consensus algorithms, especially the one we adopted---HoneyBadgerBFT,
% fall apart when there is dynamic corruption.
% In order to enforce that the corrupted machines do not change when running an instance of some Byzantine consensus algorithm,
% we introduce synchrony.

% We make use of a global clock... TODO

% Dynamic corruption only between different clock ticks is enforced by the control function.

% \subsubsection{Static corruption versus dynamic corruption}
% A subtlety exists when modelling the type of corruption.
% In dynamic corruption\footnote{In \cite{canetti2001universally}, dynamic corruption is termed Byzantine corruption.},
% $\A$ take full control of a number of machines and also learns all of their states.
% The states include private keys.
% Thus, using the dynamic corruption model from \cite{canetti2001universally} we cannot guarantee security as
% $\A$ can corrupt different machines over time and eventually learn all the private keys..

% First is to use static corruption, where the corrupted machines are fixed.
% While this circumvents our problem, it is a much weaker model.
% Alternatively, we modify the aforementioned dynamic corruption model and weaken the adversary's abilities.
% In particular, we introduce that forgetful adversary that only remembers the state of the currently corrupted nodes and forget the state of the recovered nodes.

>>>>

\section{System Architecture}

@@

\subsection{Model and assumptions}
\label{sec:model-assumptions}

@@

\subsection{Extended TrustChain}
The primary data structure used in our system is the Extended TrustChain.
Each node $u$ has a public and private key pair---$pk_u$ and $sk_u$, and a chain $B_u$.
The chain consist of blocks $B_u = \{ b_{u, i} : i \in \{ 0, \dots, h - 1 \} \}$,
where $b_{u, i}$ is the $i$th block of $u$,
and $h$ is the height of the block (i.e. $h = |B_u|$).
We often use $b_{u, h}$ to denote the latest block.
There are two types of blocks, TX blocks and CP blocks.
If $T_u$ is the set of all TX blocks in $B_u$ and $C_u$ is the set of all CP blocks is $B_u$,
then it must be the case that $T_u \cup C_u = B_u$ and $T_u \cap C_u = \varnothing$.
The notation $b_{u, i}$ is generic over the block type.
We assume there exists a function $\textsf{typeof}: B_u \rightarrow \{ \tau, \gamma \}$ that returns the type of the block,
where $\tau$ represents the TX type and $\gamma$ represents the CP type.

@@

\subsection{Consensus Protocol}
\subsubsection{Bootstrap phase}
\label{sec:bootstrap}
Now we have all the necessary information to describe our consensus protocol.
As with all distributed systems, there must be a bootstrap phase which sets up the system.

@@

\subsubsection{Consensus phase}
\label{sec:consensus-phase}
The consensus phase begins when $\F_r$ is available to all the nodes.
Note that $\F_r$ indicates the facilitators that were elected using results of round $r$ and are responsible for driving the ACS protocol in round $r + 1$.
The goal is to reach agreement on a set of new facilitators $\F_{r + 1}$ that satisfies the four properties in \Cref{def:consensus}.

@@

\subsection{Transaction Protocol}
\label{sec:tx-protocol}

@@

\subsection{Validation protocol}
\label{sec:vd-protocol}

@@

\subsubsection{Validity definition}
A transaction can be in one of three states in terms of validity---\emph{valid}, \emph{invalid} and \emph{unknown}.
Given a fragment $F_{v, j}$, the validity of the TX block $t_{u, i}$ and the agreed fragment of it is captured by the function $\textsf{get\_validity}(t_{u, i}, F_{u, i}, F_{v, j})$ (\Cref{alg:get-validity}).
Note that $t_{u, i}$ and $F_{u, i}$ are assumed to be valid,
otherwise the node calling the function would have no point of reference.
This is not difficult to achieve.
Typically the caller is $u$, so it knows its own TX block and the corresponding agreed fragment.
If the caller is not $u$, it can always query for the agreed fragment that contains the transaction of interest from $u$.

@@

\begin{algorithmic}

@@

\subsubsection{Validation protocol}
Our validation protocol,
shown in~\Cref{alg:vd-proto},
is designed to classify transactions according to the aforementioned validity definition.
If $u$ wishes to validate some TX with ID $txid$ and counterparty $v$, it sends $\langle \texttt{vd\_req}, txid \rangle$ to $v$.
The desired properties of the validation protocol are as follows.
\begin{definition}
\label{def:validation}
\textbf{\emph{Properties of the validation protocol}}

@@

\subsection{Design variations and tradeoffs}
\label{sec:tradeoffs}

@@

\subsubsection{Using epidemic protocol to reduce communication cost}
One of the final steps in our consensus protocol is to broadcast the consensus result and signatures to every other node (\Cref{sec:consensus-phase}).
While this guarantees delivery (since we assumed reliable channel), it is wasteful.
For example, if every facilitator is honest, a node would receive $n$ consensus results which are identical when only one is necessary.
Furthermore, realistic networks do not offer a broadcast primitive,
i.e. firewalls may block incoming messages from certain nodes.

@@

\subsubsection{Using timing assumption in the permissionless setting}
\label{sec:permissionless}
Our model is purely asynchronous, where we make no timing assumptions anywhere in the protocol.
However, in many applications it is often fine to make timing assumptions.
For example, TCP relies on timeout for its retransmission and the \texttt{nLockTime} property in Bitcoin transactions makes the transaction unspendable until some time in the future (either Unix time or block height)~\cite{bitcoindevguide}.
One limitation of our system is that we use the parameter $N$ in our algorithms, which makes it unsuitable for the permissionless environment where users can join and leave at will.
In this section we show how making a timing assumption would allow us to operate in the permissionless setting.

@@

\subsubsection{Privacy preserving validation protocol using compact blocks}
\label{sec:compact}
Our approach already has privacy preserving features in comparison to early blockchain systems.
That is, the transactions for each node are only revealed during the validation protocol.
Hence if two nodes never directly or indirectly interact with each other,
their transactions are never revealed.

We can take our privacy-preserving property one step further by introducing another level of hash pointer indirection.
The result is shown in~\Cref{fig:compact}.
\begin{figure}
    \includegraphics[width=0.7\linewidth]{compact}
    \centering
    \caption{The chain on the left represent direct chaining, where the digest in ``Prev'' is simply the digest of the previous block.
    The chain on the right uses compact blocks, represented by the smaller squares.
    Compact blocks also form a chain as before, but they each have a hash pointer to the full block, identified by ``Seq'' and ``Digest''.}
    \label{fig:compact}
\end{figure}

@@

\subsubsection{Optimising validation protocol using cached agreed fragments}
\label{sec:caching}
One more way to improve the efficiency of the validation protocol is to use a single agreed fragment to validate multiple transactions.
Concretely, upon receiving an agreed fragment from node $A$,
rather than validating a single transaction,
we attempt to validate all transactions with $A$ in the unknown state in that fragment.

@@

\subsubsection{Global fork detection}
The validation algorithm guarantees that there are no forks within a single agreed fragment.
This is sufficient for some applications such as proving the existence of some information.
However, for applications such as digital cash where every block depends on one or more previous blocks,
our scheme is not suitable.
For such applications, we need to guarantee that there are no forks from the genesis block leading up to the TX block of interest.

@@
